### 2013-12-09 paper/paper.tex

For example, in Experiment 2 \footnote{Demonstration movie from the authors is available at \url{http://tinyurl.com/kcdckbs}} the subjects controlled a green disc with mouse and tried to avoid contact with a white circle which chased the green circle. 

@@

Even though the subjects were explicitly told to ignore the darts, they were worse at escape in trials where the darts pointed toward green circle. 

@@

@@

@@

In Experiment 4 we assume that subjects estimated the critical distance to the surrounding agents. 

@@

@@

We expect that the locations chosen by subjects will be displaced in direction away from the wolf. 

@@

@@

@@

%ms soll ich in der Einfuhrung auch die letzte Aufgabe mit statischen Stimuli erwahnen?
%ms TODO verwendung der bezeichnungen agent, object, dart, bug fur muss ich noch vereinhaltlichen, genauso green circle und chasee und origin shift- manipulated displacement, welche noch?

\section*{General Methods}
\subsection*{Subjects}
Forty one psychology students (seven male) participated in the study in exchange for a course credit.
All subjects had normal or corrected to normal vision.

\subsection*{Stimulus}
The Stimulus programming followed the description in \cite{gao10} and the examples provided on Brian Scholls web-page. 
The display was divided into four quadrants, each forming a square of 5.9 degrees. 
Three white objects (1.9 degrees in diameter) moved inside each quadrant. 
These objects were either bugs (Experiment 1) or darts (Experiment 2). 
A bug was a circle that had two red eyes drawn on top of it. 
(These were two red circles of size 0.19 degrees, located 0.71 degrees from the center of the white circle and 0.49 degress apart.) 
The dart was a white polygon with four vertices. 
Three of them were located at the perimeter and the remaining vertex was at the origin of the circle. 
The wings of the dart formed an angle of 120 degrees.
The subject steered a a green circle (chasee, 1.2 diameter) with computer mouse. 
The movement was confined to lie within a circular area of 11.75 degrees radius. 
The boundary of the circular area was shown on the screen as a thin gray line. 
The motion of the white objects was generated as follows. 
The objects moved at constant speed of 7.8 degrees per second. 
Each object changed its direction at random intervals with 3 direction changes per second on average. 
The new direction was chosen randomly from a range of -45 to 45 degrees around its current direction. 
The objects were pervasive to each other and upon touching the wall of the designated quadrant they bounced off. 
As in \cite{gao10} when the green circle overlapped with a white agent the surface of the agent turned red. 
After testing subjects with bugs we got the impression that the red color doesn't motivate subjects enough. 
We therefore added a beep tone which sounded whenever collision happened and as long as the two shapes overlapped (see section \ref{sec:rep} for more details).\\
The orientation was manipulated as follows. 
Agents were oriented either with their eyes/nose directed towards the agent's location or perpendicular to the agent. 
There were two quadrants with perpendicular orientation and two quandrants with head-on oriented agents (wolfpack). 
The layout of the quadrants was chosen randomly on each trial. \\

@@

@@

\subsection*{Procedure}
Before block 1 and block 3 subjects were given written instruction.
Then subjects were seated 50-70 cm away from screen (all specifications in degrees of visual angle are referenced to 50 cm distance) of a Tobii T60 display with built-in remote eye-tracker. 
Upon the conclusion of the experiment the subjects were debriefed and dismissed. 
Each block lasted 15 minutes and there was a brief break between the blocks.\\
The experiment was presented and controlled with PsychoPy 1.77 \cite{peirce07} and Tobii SDK 3.0.

@@

\subsection*{Statistical Modeling}
In the analyses reported below we follow the approach advocated in \cite{gelman07} and \cite{gelman12}. 
We first design a model that appropriately describes the data. 
We use posterior predictive checking to decide whether the model is acceptable. 
We start by fitting simple model usally a model with separate parameters for each subject. 
We then design a hierarchical model that pools data across subjects \cite{lee11a}. 
Hierarchical models are most easily formulated and evaluated within bayesian framework.
Finally we report and interpret the estimates of variables of interest - usually the population-level estimates. 
We report the mean estimate and the 95 \% interval.\\
The main advantage of this approach is that it gives us flexibility to design complex models that match (or at least approach) the complexity of the processes that generated the data.
The model design involves decisions which may considerably alter the posterior estimates and even the conclusions of the analysis.
We discuss some of these modeling decisions in the Results section below. In general, virtually all results held at least to some degree across all the various models we evaluated and as such the main conclusions of this report are robust.\\
An overview of the models from which we report estimates is given in table \ref{tab:models}. 
Bayesian model requires formulation of prior distributions for the analysis. 
These are not included the table. 
We selected priors such that they do not influence the results of estimation. 
Usually we chose uniform priors, constrained to reasonable range of parameter values (e.g. range $[0,1]$ for mean proportion $\mu_{\mu}$ in S2.2). 
The models were evaluated with STAN 2.0.1 which fits statistical models with Markov chain Monte Carlo sampling. 
In each analysis, four chains were run and the convergence was checked by computing for each parameter an estimate of the potential scale reduction $\hat{R}$ (see \cite{gelman03} p.297). 
In all analyses and for all parameters we ensured that $\hat{R} \leq 1.2$ where $\hat{R} = 1$ upon convergence.
The analyses are documented and can be replicated with the IPython Notebooks available from the project repository.
The table \ref{tab:ip} links the reported analyses to the output in these files. 
\section*{Results}

>>>>

%bt ... "were more difficult"  die Aufgabe war schwieriger zu bewältigen? woran zeigte sich das? evtl. hier kurz die AV erwähnen
For example, in Experiment 2 \footnote{Demonstration movie from the authors is available at \url{http://tinyurl.com/kcdckbs}} the subjects controlled a green disc with a computer mouse and tried to avoid contact with a white circle which chased the green circle.

@@

Even though the subjects were explicitly told to ignore the darts, they were worse at escaping in trials where the darts pointed toward green circle. 

@@

%bt Allgemeine Anmerkung: Ich hatte den Eindruck, dass die Begriffe displacement und motion manchmal in verschiedenen Bedeutungen verwendet werden. Displacement nennst Du die Verschiebung des Rotationspunkts. Wenn ich das alles richtig verstanden habe gehts darum, dass diese Verschiebung dazu führt, dass die Rotation dann als Bewegung (motion) wahrgenommen wird, richtig? Müsste dann in dem SAtz nicht stehen ...the manipulated orientation change has to be perceived as an orientation change and not as motion? Vielleicht habe ichs aber auch nur noch nicht ganz kapiert...

@@

%bt Anmerkung zur Fugure 2: Evtl. den grünen Punkt nicht grün anzeigen, da man sonst meinen könnte, dies wäre der grüne Circle, den die Vpn steuert (zugegeben, das wären dumme Leser, aber man weiß ja nie...) 

@@

We assume that in Experiment 4 subjects estimated the critical distance to the surrounding agents. 

@@

%bt das klingt ein wenig so, als ob wir zwingend eine solche ALternativerklärung annehmen müssen... habe aber auch keine bessere Formulierung.

@@

We expect that the locations chosen by subjects will be displaced in direction away from the Chasee. 
%bt habe wolf rausgenommen, um die Bezeichnungen der Stimuli möglichst konstant zuhalte - macht es für den Leser einfacher.

@@

%bt dieser Abschnitt (oben ab ---on the other hand) ist schweirig nachzuvollziehen. Evtl. kann man dieses Arguemtn besser verstehen nachdem die Aufgaben beschrieben wurden.

@@

%bt dieser Satz sollte auch unbedingt im Abstract so ähnlich auftauchen, da er die Hauptpunkte der Studien super zusammenfasst und den Mehrgewinn gegenüber den bisherigen Arbeiten darelgt.

@@

%ms soll ich in der Einfuhrung auch die letzte Aufgabe mit statischen Stimuli erwahnen?
%bt Halte ich in der Einführung nicht für zwingend - würde nur verwirren.
%ms TODO verwendung der bezeichnungen agent, object, dart, bug fur muss ich noch vereinhaltlichen, genauso green circle und chasee und origin shift- manipulated displacement, welche noch?
% bt stimmt, damit erledigt sich meine Anmerkung oben.

\section*{General Methods}
\subsection*{Subjects}
Forty one psychology students (seven male) participated in the study in exchange for a course credit.
All subjects had normal or corrected to normal vision.
%bt Altersangaben sollten noch rein (Mittleres alter und Range). Waren das wirklich nur 7 männliche Teilnehmer?

\subsection*{Stimuli}
The Stimulus programming followed the description in \cite{gao10} and the examples provided on Brian Scholls web-page. 
The display was divided into four quadrants, each forming a square of 5.9 degrees. 
Three white objects (1.9 degrees in diameter) moved inside each quadrant. 
These objects were either bugs (Experiment 1) or darts (Experiment 2). 
A bug was a circle that had two red eyes drawn on top of it. 
(These were two red circles of size 0.19 degrees, located 0.71 degrees from the center of the white circle and 0.49 degress apart.) 
The dart was a white polygon with four vertices. 
Three of them were located at the perimeter and the remaining vertex was at the origin of the circle. 
The wings of the dart formed an angle of 120 degrees.
The subject steered a a green circle (chasee, 1.2 diameter) with computer mouse. 
The movement was confined to lie within a circular area of 11.75 degrees radius. 
The boundary of the circular area was shown on the screen as a thin gray line. 
The motion of the white objects was generated as follows. 
The objects moved at constant speed of 7.8 degrees per second. 
Each object changed its direction at random intervals with 3 direction changes per second on average. 
The new direction was chosen randomly from a range of -45 to 45 degrees around its current direction. 
The objects were pervasive to each other and upon touching the wall of the designated quadrant they bounced off. 
As in \cite{gao10} when the green circle overlapped with a white agent the surface of the agent turned red. 
After testing subjects with bugs we got the impression that the red color doesn't motivate subjects enough. 
We therefore added a beep tone which sounded whenever collision happened and as long as the two shapes overlapped (see section \ref{sec:rep} for more details).\\
The orientation was manipulated as follows. 
Agents were oriented either with their eyes/nose directed towards the agent's location or perpendicular to the agent. 
There were two quadrants with perpendicular orientation and two quandrants with head-on oriented agents (wolfpack). 
The layout of the quadrants was chosen randomly on each trial. \\

@@

%bt sind es 3 Blocks oder 4 Blocks? Wenn in jedem Block 42 trials enthalten sind, dann müssten es 4 Blocks sein, sonst gibst Probleme an der Stelle wo Du in Block 3 die 18 und die 24 trials beschreibst und danach noch die 13 letzten trials. Du kannst von 3 Hauptblöcken schreiben und die letzten 13 trials als final oder addtional block einführen, dann musst Du nicht schon vorher detailliert darauf eingehen.

@@

\subsection*{Procedure}
Before block 1 and block 3 subjects were given written instruction.
%bt evtl. umstellen. Erst beschreiben, wie die Vpn sitzt und dann auf die Instruktionen eingehen.
Then subjects were seated 50-70 cm away from screen (all specifications in degrees of visual angle are referenced to 50 cm distance) of a Tobii T60 display with built-in remote eye-tracker. 
Upon the conclusion of the experiment the subjects were debriefed and dismissed. 
Each block lasted 15 minutes and there was a brief break between the blocks.\\
The experiment was presented and controlled with PsychoPy 1.77 \cite{peirce07} and Tobii SDK 3.0.

@@

\subsection*{Statistical Modeling}
In the analyses reported below we follow the approach advocated in \cite{gelman07} and \cite{gelman12}. 
We first design a model that appropriately describes the data. 
We use posterior predictive checking to decide whether the model is acceptable. 
We start by fitting simple model usally a model with separate parameters for each subject. 
We then design a hierarchical model that pools data across subjects \cite{lee11a}. 
Hierarchical models are most easily formulated and evaluated within bayesian framework.
Finally we report and interpret the estimates of variables of interest - usually the population-level estimates. 
We report the mean estimate and the 95 \% interval.\\
The main advantage of this approach is that it gives us flexibility to design complex models that match (or at least approach) the complexity of the processes that generated the data.
The model design involves decisions which may considerably alter the posterior estimates and even the conclusions of the analysis.
We discuss some of these modeling decisions in the Results section below. In general, virtually all results held at least to some degree across all the various models we evaluated and as such the main conclusions of this report are robust.\\
An overview of the models from which we report estimates is given in table \ref{tab:models}. 
Bayesian model requires formulation of prior distributions for the analysis. 
These are not included the table. 
We selected priors such that they do not influence the results of estimation. 
Usually we chose uniform priors, constrained to reasonable range of parameter values (e.g. range $[0,1]$ for mean proportion $\mu_{\mu}$ in S2.2). 
The models were evaluated with STAN 2.0.1 which fits statistical models with Markov chain Monte Carlo sampling. 
In each analysis, four chains were run and the convergence was checked by computing for each parameter an estimate of the potential scale reduction $\hat{R}$ (see \cite{gelman03} p.297). 
In all analyses and for all parameters we ensured that $\hat{R} \leq 1.2$ where $\hat{R} = 1$ upon convergence.
The analyses are documented and can be replicated with the IPython Notebooks available from the project repository.
The table \ref{tab:ip} links the reported analyses to the output in these files. 
\section*{Results}
%bt ich habe jetzt nicht ganz aufgepasst. Bleibst Du bei der Beschreibung der REsults in der Reihenfolge wie die Aufgaben auch gestellt wurden? Wenn nicht wäre es gut, einen Satz zu schreiben, warum Du welche Ergebnisse vorziehst.
